Approximate State Abstraction

### 2016-01-30 paper/paper.tex
Fixed typo
Started on formalizing Phi_model but didn't get that far :/

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand\defn[1]{{\bf Definition:} #1}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}

@@

Thus, our base case and induction we conclude that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{model}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
\end{equation}

{\bf Proof:}

Let the maximum upper bound between optimal behavior in the noisy and ground MDP be called $B_s$.

@@

{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
\end{equation}

@@

{\bf Lemma 5:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
\end{equation}

>>>>

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand{\epM}{\ep_{\text{model}}}
\newcommand\defn[1]{{\bf Definition:} #1}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

@@

\enote{Define $V_G$ and $V_A$ (value function in ground and value function in abstract)}
\enote{Say more about the weighting (that is sums to 1 but that's all we assume)}

@@

Thus, from our base case and induction we conclude that
\begin{equation}
\forall_{t, g \in \mathcal{S}_g} V^{\pi^*}(g) \leq  V^{\pi_{A,t}}(g) + \sum_{i=0}^{t}\gamma^i \frac{2\epsilon}{1-\gamma}
\end{equation}

@@

{\bf Lemma 2:} When $S_A$ is created using a function of the $\ep_{model}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{{\epsilon_{\mathcal{R}}} + \gamma |\mathcal{S}|\epsilon_{\mathcal{T}}}{(1-\gamma)^3}
\end{equation}

{\bf Proof:}
Given the ground \ac{MDP}, $M_G$, consider the \ac{MDP}, $M_G'$ which is identical to $M_G$ except in its transition and rewards.

\begin{equation}
M_G' =  \langle \mathcal{S}_G, \mathcal{A}, \mathcal{R}_G', \mathcal{T}_G', \gamma \rangle
\end{equation}

Where
\begin{align}
\mathcal{R}_G'(s,a) = R_A(\epM(s), a)\\
\mathcal{T}_G'(s,a, s') = R_A(\epM(s), a, \epM(s'))
\end{align}

We know by \cite{li2006towards} that .

Let the maximum upper bound between optimal behavior in the noisy and ground MDP be called $B$.

@@

{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
\end{equation}

@@

{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
\end{equation}
